Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2014-09-26 article.Rmd
Facet reviewers by subfield

```{r load-libraries, include=FALSE}
options(stringsAsFactors = FALSE)
library(genderdata)
library(gender)
library(dplyr)
library(ggplot2)
library(mullenMisc)
library(knitr)
library(stringr)
library(scales)
library(tidyr)
library(ggthemes)
library(RColorBrewer)

@@

# I like 
article_theme <- theme(legend.title = element_blank()) + theme_few()

@@

**Cameron: Do you have the mapping you use from the AHR's 68 categories to the 8 or so you used? With that, I just have one or two more lines to facet this plot. (It doesn't look right because it's not faceted yet.)**

```{r}
ahr_predicted %>%
  filter(gender_author == "female") %>%
  select(year, gender_reviewer, category) %>% 
  group_by(year, gender_reviewer, category) %>%  
  summarize(n = n()) %>%
  spread(gender_reviewer, n, fill = 0) %>% 
  mutate(female_proportion = female / (female + male + unknown),
         male_proportion = male / (female + male + unknown),
         unknown_proportion = unknown / (female + male + unknown)) %>%  
  select(female_proportion, male_proportion, unknown_proportion,
         year, category) %>% 
  gather(gender, proportion, -year, -category) %>%
ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Gender of reviewers of female book authors in AHR by category") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette,
                    labels = c("Female", "Male", "Unknown")) +
  article_theme +
  short_scale
```

>>>>

```{r load-libraries, include=FALSE}
library(genderdata)
library(gender)
library(dplyr)
library(ggplot2)
library(mullenMisc)
library(knitr)
library(stringr)
library(scales)
library(tidyr)
library(ggthemes)
library(RColorBrewer)

@@

# I like 
article_theme <- theme(legend.title = element_blank(),
                       strip.background = element_rect(color = "white")) +
  theme_classic()

@@

```{r reviews-by-category}
categories <- read.csv("data/ahr-categories.csv", stringsAsFactors = FALSE)

ahr_predicted %>%
  left_join(categories, by = "category") %>%
  filter(gender_author == "female",
         !our_category %in% c(NA, 
                              "Latin and South America, Carribean",
                              "Middle East")) %>%
  select(year, gender_reviewer, our_category) %>% 
  group_by(year, gender_reviewer, our_category) %>%  
  summarize(n = n()) %>%
  spread(gender_reviewer, n, fill = 0) %>% 
  mutate(female_proportion = female / (female + male + unknown),
         male_proportion = male / (female + male + unknown),
         unknown_proportion = unknown / (female + male + unknown)) %>%  
  select(female_proportion, male_proportion, unknown_proportion,
         year, our_category) %>% 
  gather(gender, proportion, -year, -our_category) %>%
ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  facet_wrap(~ our_category) +
  xlim(1970, 2012) +
  ggtitle("Gender of reviewers of female AHR authors by category, 1970-2012") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette,
                    labels = c("Female", "Male", "Unknown"),
                    name = "Gender") +
  article_theme +
  theme(strip.background = element_rect(color = "white"))
```
